### 2024-03-26 doc/sections/mav-syntax.tex
Define symmetric core

We write $\vInferFrom*$ for the reflexive, transitive closure of $\vInferFrom$.
We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.

>>>>

We write $\vInferFrom*$ for the reflexive, transitive closure of $\vInferFrom$.
We write $\vBiInfer$ for the symmetric core of $\vInferFrom$ (\ie ${\vBiInfer} = {\vInferFrom\cap\vInferTo}$) and $\vBiInfer*$ for the reflexive, transitive closure of $\vBiInfer$.
